SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-07 sedona-ieice16/revision/reviews/review_response.tex

\clearpage
\section*{Reviewer}\label{sec:rev1}

% 1
\rev{
$<<$ Reviewer's comments to the author(s) $>>$

The SEDONA is based on the probability that any daemons run during the
measurement. And cutoff time is based on the actual measurement time.
The proposed approach is interesting, but I cannot understand why the
author employs such statistics and heuristic way, and how efficient the
proposed approach will work. Please refer to my comments, and consider
to revise the manuscript and re-submit .
}

Your concerns are well understood. 
Indeed, our statistics and heuristics greatly help us 
identify what daemons are infrequent, long-running on our system 
(as described in the fourth paragraph in the left column on page~3). 
Applying such statistics and heuristics can be done to any Linux system, 
which make our protocol generic. Furthermore, the experimental results show that 
our protocol is more efficient than the traditional method relying on elapsed time.

Note that my responses to your comments 
are incorporated into the revision and marked in {\color{red}red}. 
There are some new and modified contents in the revision, 
which are marked in {\color{blue}blue} for better distinction.

I now respond to individually below.

@@

\rev{ 
(3) The improvement of the SEDONA is little. And the extent of the each
benchmark’s improvement described in Table 3 varies widely. Thus, the
experimental results does not confirm whether the SEDONA is widely
practical or is useful.
}

This review is basically the same as (2). Please refer to our response of (2) for this comment. 
One note. You may feel that the extent of the improvement varies widely, 
because the SPEC CPU2006 includes a set of very different compute-bound benchmarks. 
But even if so, we found that all the benchmarks in the suite benefited from our timing protocol, 
and in addition, for some workloads, our protocol significantly reduced their variability up to by 10x.

\rev{ 
(4) Since the explanation of ``dual-PUT'' is not enough, I can not well
understand the algorithm shown in Fig. 3. Similarly, what is “1st
Half’s ET (ms)” attached at Fig. 4(b), 4(c), 4(d) ? I understood only that
the label is related with “dual-PUT”. These words are important in the
manuscript. So, please keep in mind to write understandably.
}

Your point is well taken. 
The term of ``dual-PUT'' represents 
a pair of two consecutive samples of a run of a (regular) PUT. 
(The task length of that regular PUT is virtually doubled, extended to the corresponding 
dual-PUT.) More descriptions of the term ``\hbox{dual-PUT}'' are provided with a simple example in the second paragraph in the right column on page~2. 
In addition, the 1st half indicates the first element of the pair 
whereas the 2nd half the second element of the same pair. 
The label of ``1st Half's ET (ms)'' is renamed as ``Odd Samples' ET(ms),'' 
for better clarification. Please refer to the subsequent (third) paragraph.

### 2017-02-07 sedona-ieice16/revision/cover_letter.tex
Revision done

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
\hfill Supercomputing R\&D Center, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI), 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: yksuh@kisti.re.kr
\end{flushright} 
%\vfill % forces letterhead to top of page

%\vspace{-0.5in}

\opening{Dear Editor-in-Chief:}

\noindent This letter to be submitted to IEICE Transactions on Information and Systems 
presents the following contributions. No version of this letter was submitted earlier.

\begin{itemize}

\item We provide empirical evidence that measuring program time 
can be seriously affected by extant system daemons.

\item We propose a novel timing protocol, called {\em SEDONA} (Selective Elimination through Detection of infrequent, lOng-ruNning dAemons), 
that identifies infrequent, long-running daemons that impact the timing results for that program.

\item We evaluate the performance of the protocol with rigorous experiments, starting from a simple program in pure-computation mode 
to a popular industrial benchmark suite.

\item Experimental results show a strong support for the effectiveness of our SEDONA timing protocol. 
\end{itemize}

>>>>

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
%\hfill National Institute of Supercomputing and Networking, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI), 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: youngkyoon.suh@gmail.com
\end{flushright} 
%\vfill % forces letterhead to top of page

\vspace{0.5in}

\opening{Dear Prof. Rajkumar Buyya:}

\noindent

Attached is a minor revision that responds to the first reviewer's comments. 
We marked in red some text in response to his/her comments. 
The revision also includes some texts marked in blue that are added or updated. 
Note also that we replaced the term of {\em PUT} with another term, called {\em INC}, 
in order to prevent readers from getting confused with a general concept of the program under test. 
Many thanks to you for taking sincere care of our manuscript during a series of reviews.
